Reviewer Comments (Scientific Reports)

### 2020-01-25 notebook/sci_rep_reviews.Rmd
Some more analytical playing, and rho results

Reviewer 2 comments
================================================================================

@@

@@

>>>>

Reviewer 2 comment 1
================================================================================

@@

I thank Reviewer 2 for their helpful comments. In my revision, I have provided more analytical context, expanded the types of networks explored (see also Author response to Reviewer 1 comment 3), and further clarified the role response rate variation. I explain these changes in more detail with the reviewers elaborated concerns below.

Reviewer 2 comment 2
================================================================================

@@

I appreciate these comments, and have tried to provide a more analytical explanation of the changes introduced by \gamma (line XXX). In making these changes, I have slightly adjusted the notation so that the text is more readable.

As Reviewer 2 correctly points out, my focus is on finite values of S and \sigma, in which complexity is gradually increased until it is dangerously close to the stability boundary. Given this focus, analytically demonstrating my central result (that variation in $X$ when $M = XA$ increases stability) would require some sort of comparison between the probability distributions of eigenvalues for $M$ and $A$. For circular matrices in which elements are i.i.d ($A$), it has been proved that eigenvalues are distributed uniformly within a known boundary of support of the spectral density (Tao and Vu 2010). While recent papers have found the support for more general types of random matrices that include the form $M = AX$ (e.g, Gibbs et al. 2018; Neri and Metz 2012; Ahmadian et al. 2015), to the best of my understanding, finding the actual density of eigenvalues within the support has not been attempted. This likely matters because for finite S, even though the real boundary of the support might be positive for both $M$ and $A$ (implying instability as $S \to \infty$; Grilli et al. 2017), the right most eigenvalue for a system still might be less than zero.

My approach follows others with similar goals (Sinha 2005).

Others have found the support

Reviewer 2 is correct that analytical results here are uncharted territory, despite

In recent papers, analytical solutions have been provided to find the support of the spectral densities of matrices of the form $M = XA$,

This is unique, as most studies make the simplifying assumption of \sigma = \sqrt{S} such that the circular matrix has a radius of unity.

Ideally, an analytical proof could demonstrate the uncertainty in the position of the leading eigenvalue at finite S, which would likely require knowledge of the distribution of M = \gamma A for arbitrary values of \sigma and S.

For matrices of the form $M = XA$, Gibbs et al. (2018) do find the boundaries of support for spectral densities.

My focus is uniquely on a finite S. This is important, as Ahmadian et al. (2015) showed that any realisation of the eigenvalue distribution for a matrix of the form Z = M + LJR approaches the expected distribution as S \to infty.

Elements of M = XA are no longer independent.
